\subsection{Purpose and scope}

This is the Implementation and Test Deliverable document, its purpose is to explain the implementation and testing process for the SafeStreets system based on the RASD and DD documents.
In the following section the topics to be covered are:

\begin{itemize}
    \item 
    An overview of the proposed architecture
    \item 
    Implemented requirements and their motivation
    \item 
    Adopted development frameworks, along with their advantages and disadvantages.
    \item 
    The structure of the source code
    \item 
    Testing
    \item 
    Installation instructions
\end{itemize}

\subsection{Definitions, Acronyms, Abbreviations}

\subsubsection{Definitions}
\begin{itemize}
    \item Traffic violation: An action performed by a driver of a vehicle which is against the local traffic regulations.
    \item Report: Information submitted by a user to notify the system and, by extension, authorities of a traffic violation.
    \item Authority: A local agency whose purpose is, as indicated by the current law, to enforce traffic rules. For example: the police.
    \item Ticketing system: A government database containing information about issued traffic tickets.
    \item License plate registry: A government database connecting a license plate with the car registered to it and information about it such as the make, model and color.
    \item Widget: Flutter UI component.
\end{itemize}

\subsubsection{Acronyms}
\begin{itemize}
    \item API: Application Programming Interface.
    \item HTTP: HyperText Transfer Protocol.
    \item HTTPS: HyperText Transfer Protocol Secure.
    \item UI: User Interface.
    \item RASD: Requirements Analysis and Specification Document.
    \item DD: Design Document.
\end{itemize}

\subsubsection{Abbreviations}
\begin{itemize}
    \item {[FRn]}: n-th functional requirement
    \item {[SRn]}: n-th security requirement
\end{itemize}