\subsection{Purpose and Scope}

The purpose of this document is to describe the focus of the acceptance tests performed on the prototype of SafeStreets developed by another group of students.
The topics covered are:
\begin{itemize}
    \item 
    Description of the project to be analysed.
    \item 
    The installation process performed in order to run the prototype.
    \item
    Acceptance tests cases considered and applied to the application.
    \item
    Other aspects to consider, concerning the quality of documentation and code.
\end{itemize}

\subsection{Definitions and Acronyms}
\subsubsection{Definitions}
To keep the same context and idea for the application, in this document we will use the same definitions as the team who developed the project.

\begin{itemize}
    \item System: The software developed.
    \item User: A person that uses the system.
    \item Normal user: A person that uses the system which is not responsible for the streets’ security
    \item Authority: A person employed by the municipality who is responsible for the security of the streets’ network.
    \item Area: A district of a city consisting in a collection of streets which are connected together and which have a horizontal extension similar to the vertical extension.
\end{itemize}

\subsubsection{Acronyms}
\begin{itemize}
    \item
    RASD: Requirement Analysis and Specification Document
    \item
    DD: Design Document
    \item
    ITD: Implementation and Testing Deliverable
    \item
    UI: User Interface
\end{itemize}

\subsection{Revision history}

\begin{itemize}
    \item Version 1.0: First release
\end{itemize}